Improved Smooth Free-Form Deformation with Sharp Feature Awareness

### 2016-08-25 paper.tex
add some translate from the cui to mine

\textcolor{red}{FFD, which was first proposed by Sederberg and Parry \cite{Sederberg86}, is an intuitive model manipulation and soft
object animation method. The main concept of FFD is to embed the object into an intermediate space, e.g., a B\'ezier
volume. Users first edit the shape of the intermediate space; then, the space deformation is transferred to the embedded
object, whereas the topological connectivity of the object remains unchanged. There are many successive studies
regarding FFD. Most of these studies focus on improving the interactive means of FFD \cite{Coquillart90, Hui02,
MacCracken96, McDonnel07, Xu13}. Gain and Bechmann~\cite{Gain08} provided a detailed survey of these methods.}

@@

>>>>

\textcolor{red}{FFD, which was first proposed by Sederberg and Parry \cite{Sederberg86}, is an intuitive model manipulation and soft
object animation method. The main concept of FFD is to embed the object into an intermediate space, e.g., a B\'ezier
volume. Users first edit the shape of the intermediate space; then, the space deformation is transferred to the embedded
object, whereas the topological connectivity of the object remains unchanged. There are many successive studies
regarding FFD. Most of these studies focus on improving the interactive means of FFD \cite{Coquillart90, Hui02,
MacCracken96, McDonnel07, Xu13}. Gain and Bechmann~\cite{Gain08} provided a detailed survey of these methods.}
\textcolor{green}{
    FFD is an very intuitive method used to deform model or animate soft object. It was first proposed by Sederberg and Parry \cite{Sederberg86} and have inspired many researchers to proposed a series of methods base on the FFD. Gain and Bechmann~\cite{Gain08} provided a detailed survey of these methods. The main idea of FFD is embedding the model into an intermediate space like B\'ezier volume. The intermediate space can be edited by user, then it will transfer the deformation to the embedded model. While the topological connectivity of the model can be reserved during the deformation. However, most of the existing methods focus on the interactive means of FFD but not the quality of the deformation result.
}

@@

\textcolor{green}{
}
